Towards Automated Refactoring of Code Clones in Object-Oriented Programming Languages\\- Work in Progress -

### 2019-07-03 sattose/paper.tex
PDF figures
All charts pdf now
Ana

\section{Introduction}
Duplication in source code is often seen as one of the most harmful types of technical debt. In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}. A paper by Bruntink et al.~\cite{bruntink2005use} shows that code clones can contribute up to 25\% of the code size, which has a negative impact on the maintainability.
% In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve the maintainability of the refactored code.

@@

\begin{figure}[H]
  \caption{Amount of times a clone with a certain number of tokens has a certain number of nodes.}
    \includegraphics[width=.95\columnwidth]{img/TokenThreshold}
  \label{fig:tokenthreshold}
\end{figure}

@@

\begin{figure}[H]
  \caption{Number of cloned declarations/statements.}
    \includegraphics[width=.9\columnwidth]{img/TypeResults}
  \label{fig:typeres}
\end{figure}

@@

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=.9\columnwidth]{img/DurationChart}
  \label{fig:performance}
\end{figure}

>>>>

\section{Introduction}
Duplication in source code is often seen as one of the most harmful types of technical debt. In Martin Fowler's ``Refactoring'' book~\cite{fowler1999refactoring}, he claims that \textit{``If you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them.''}. Bruntink et al.~\cite{bruntink2005use} show that code clones can contribute up to 25\% of the code size, which has a negative impact on the maintainability.
% In this research, we take a look at the challenges and opportunities in automatically refactoring duplicated code, also known as ``code clones''. The main goal is to improve the maintainability of the refactored code.

@@

\begin{figure}[H]
  \caption{Amount of times a clone with a certain number of tokens has a certain number of nodes.}
    \includegraphics[width=1\columnwidth]{img/TokenThreshold}
  \label{fig:tokenthreshold}
\end{figure}

@@

\begin{figure}[H]
  \caption{Number of cloned declarations/statements.}
    \includegraphics[width=1\columnwidth]{img/TypeResults}
  \label{fig:typeres}
\end{figure}

@@

\begin{figure}[H]
  \caption{Duration in minutes of identifying clones for clone type definitions.}
    \includegraphics[width=1\columnwidth]{img/DurationChart}
  \label{fig:performance}
\end{figure}
